\begin{acknowledgements}
    At times, when working on highly theoretical research such as this thesis, it is easy to feel dissuaded or stuck. That makes it even more important to have a network of support around you that encourages you to push on through the hardest parts. I am incredibly excited to have had the opportunity to study in this field and write this thesis, and I am so deeply grateful to everyone who has helped me along the way. I could not be happier with how it has turned out, and I have my own support network to thank for that.

    First, I would like to express my deepest gratitude towards my advisor, Professor Danny Krizanc. Throughout my semesters of research, he has been a constant source of advice and support. I would never have been able to write this thesis without his wealth of knowledge and insight.
    
    I would also like to thank my reading committee, Victoria Manfredi and Sonia Roberts, for taking the time out of their schedules to consider my thesis for the honors program. It really is appreciated.

    To my incredible family, you are the reason I could write this thesis in the first place. My parents, Susan and Campbell McLaren, have supported me in every way possible as I navigated college life. My siblings, Campbell and Jacqueline McLaren, have always been there for me, encouraging me every step of the way.

    Finally, I am so thankful to all of my friends at Wesleyan and beyond. Thank you for putting up with me when I was taking as many credits as I could fit into a semester to finish my three majors.

    
    
\end{acknowledgements}