\chapter{Conclusion}
In this thesis, we have conducted a comprehensive study of the complexity of finding the second-best solution to combinatorial optimization $\nph{}$ problems, including the Traveling Salesman Problem, Maximum Clique, Minimum Vertex Cover, Set Cover, and others. Our work has significantly expanded the understanding of this important class of problems and has laid the foundation for future research in this area. We were able to find algorithms for every second-best problem in $P$ and showed reductions from existing problems for the $\nph{}$ ones.

Our results have shown that, in most cases, finding the second-best solution, let alone $k$-best solutions, to an $NP$-hard optimization problem is itself an $NP$-hard task. This holds true even when the optimal solution is provided as part of the input, highlighting the inherent difficulty of these problems. We have also identified a few notable exceptions, such as the exclusive second-best Bin Packing problem with integer output and the inclusive and exclusive second-best Constrained TSP problem, both of which can be solved in polynomial time despite the $NP$-hardness of the original problem.

One of the key contributions of our work has been the development of a general approach for proving the hardness of second-best problems. By leveraging the relationships between different optimization problems and their established reduction proofs, we have been able to produce $NP$-hardness results for a broad class of problems and lay a framework that can serve as a valuable tool for future researchers investigating the complexity of $k$-best problems. The very fact that we used our own second-best problems in reductions to other second-best problems shows the potential practicality of our work for helping to develop future hardness reductions.

Looking ahead, there are numerous exciting avenues for future research in this area. Examining the Traveling Salesman Problem,  we have not yet formalized the proof that \exob{}-Euclidean-TSP and \inob{}-Euclidean-TSP are $\nph{}$. Future work should aim to fill this gap. There are also many natural restrictions to TSP other than the simple convex shape constraint that can also make the optimization problem computable in polynomial time. For instance, Rothe published a result that graphs constrained to be a small number of parallel lines or a ``necklace tour" permit polynomial time solutions to the traveling salesman problem \cite{rothe1988two}. We would expect future work on the second-best question to explore whether these constraints also permit easy solutions to the second-best versions of TSP.


Beyond the traveling salesman, there are many other natural combinitorial optimization problems to be examined. We would look for future work to expand our results to the remaining problems in Karp's 21 $\npc{}$ problems defined in \cite{karp1972reducibility}, as well as any other $\nph{}$ problems that seem to naturally arise.

Additionally, we suspect it may be easier to find second-best solutions to optimization problems that permit approximations of arbitrary accuracy, largely considered to be "easier" problems to compute than other problems in $\nph{}$. If that was the case, it could provide a new way for approaching approximation questions, a highly practical field in current computer science research. However, we were unable to reach a conclusion on the matter at this point in time. Some specific problems that may be illustrative in this area are Maximum Planar Independent Set and the Knapsack problem.

Finally, our work has focused primarily on the second-best case, but there is much to be explored in the realm of higher values of $k$, both for specific values of $k$ and allowing for $k$ to be an variable in the input of a problem. Understanding the complexity landscape as $k$ grows and identifying potential hardness transitions or structural changes could lead to significant breakthroughs in our understanding of these problems.

In conclusion, our thesis has made significant contributions to the study of $k$-best and particularly second-best $\nph{}$ optimization problems. We have developed new problem classes, proved hardness results for a wide range of problems, and laid the groundwork for future research in this important area. As the field of optimization continues to grow and evolve, we believe that the insights and techniques developed in this work will play a crucial role in shaping our understanding of the complexity of finding not just the best, but the $k$-best solutions.

